Low-Cost Data Deduplication for Virtual Machine Backup in Cloud Storage

### 2013-03-09 hotstorage13/eval.tex
w

\begin{verbatim}
q= is chosen between 500 or 100
Memory limit:   20 30M   50M  75M  100M  200M
Time:          3.2  3.11   3  2.99 2.96  2.95
Time for two scans: 2.78 2.78 2.78 2.78 2.78
\end{verbatim}

Table~\ref{tab:memory} shows the performance data when 
the memory limit imposed on each node varies  from 20MB to 200MB.
The overall processing time does not have a significant reduction as we increase to 200MB.
As Row 2 shows, the time is mainly dominated by  the two scans of dirty VM segments.
Each scan takes about 1.4 hours.
Thus we conclude that using about 30MB is sufficient to have VM backup completed in parallel 
within about 3.09 hours.

>>>>

%\begin{verbatim}
%q= is chosen between 500 or 100
%Memory limit:   20 30M   50M  75M  100M  200M
%Time:          3.2  3.11   3  2.99 2.96  2.95
%Time for two scans: 2.78 2.78 2.78 2.78 2.78
%\end{verbatim}

\begin{figure}
\centering
\includegraphics[width=0.5\textwidth]{mem_time.pdf}
\caption{ Parallel time when memory limit imposed varies from 20MB to 200MB.}
\label{fig:memory}
\end{figure}

Figure~\ref{tab:memory} shows the performance data when 
the memory limit imposed on each node varies  from 20MB to 200MB.
The overall processing time does not have a significant reduction as we increase to 200MB.
As Row 2 shows, the time is mainly dominated by  the two scans of dirty VM segments.
Each scan takes about 1.4 hours.
Using about 30MB is sufficient to have VM backup completed in parallel 
within about 3.09 hours.
